---
title: "Final-R code-Zhiwen Xu"
output:
  html_document:
    df_print: paged
---

```{r}
library(ggplot2)
library(forecast) 
require(gdata)
library(tidyr)
library(xts)
library(readxl)
library(tseries)
library(TSA)
```

# First Dataset AMGN #

```{r}
data1 = read_xlsx ("ZhiwenXu.xlsx", sheet = 1)
data_clean1 = data1 %>% drop_na()
return1 = as.ts(data_clean1$`return`)
```

### plot the series ###
```{r}
plot(return1)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=return1,order=c(1,1))
mpq1 = garch(x=return1,order=c(1,2))
mpq2 = garch(x=return1,order=c(2,1))
mpq3 = garch(x=return1,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq1),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
res1 = residuals(mpq1)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```


### diagnostics
```{r}
# diagnostics
qqnorm(residuals(mpq1)); qqline(residuals(mpq1))
acf(residuals(mpq1)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq1)))
jarque.bera.test(na.omit(residuals(mpq1)))
skewness(na.omit(residuals(mpq1)))
kurtosis(na.omit(residuals(mpq1)))
gBox(mpq1,x=return1,method='squared')
gBox(mpq1,lags =20,plot = F, x=return1,method='squared')$pvalue
```

# Second Dataset AMGN #

```{r}
data2 = read_xlsx ("ZhiwenXu.xlsx", sheet = 2)
data_clean2 = data2 %>% drop_na()
return2 = as.ts(data_clean2$`return`)
```

### plot the series ###
```{r}
plot(return2)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=return2,order=c(1,1))
mpq1 = garch(x=return2,order=c(1,2))
mpq2 = garch(x=return2,order=c(2,1))
mpq3 = garch(x=return2,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq1),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
res2 = residuals(mpq1)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
# diagnostics
qqnorm(residuals(mpq1)); qqline(residuals(mpq1))
acf(residuals(mpq1)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq1)))
jarque.bera.test(na.omit(residuals(mpq1)))
skewness(na.omit(residuals(mpq1)))
kurtosis(na.omit(residuals(mpq1)))
gBox(mpq1,x=return2,method='squared')
gBox(mpq1,lags =20,plot = F, x=return2,method='squared')$pvalue
```

# Third Dataset AAPL #

```{r}
data3 = read_xlsx ("ZhiwenXu.xlsx", sheet = 3)
data_clean3 = data3 %>% drop_na()
return3 = as.ts(data_clean3$`return`)
```

### plot the series ###
```{r}
plot(return3)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=return3,order=c(1,1))
mpq1 = garch(x=return3,order=c(1,2))
mpq2 = garch(x=return3,order=c(2,1))
mpq3 = garch(x=return3,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq1),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
res3 = residuals(mpq1)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
# diagnostics
qqnorm(residuals(mpq1)); qqline(residuals(mpq1))
acf(residuals(mpq1)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq1)))
jarque.bera.test(na.omit(residuals(mpq1)))
skewness(na.omit(residuals(mpq1)))
kurtosis(na.omit(residuals(mpq1)))
gBox(mpq1,x=return3,method='squared')
gBox(mpq1,lags =20,plot = F, x=return3,method='squared')$pvalue
```

# Fourth Dataset AVY #

```{r}
data4 = read_xlsx ("ZhiwenXu.xlsx", sheet = 4)
data_clean4 = data4 %>% drop_na()
return4 = as.ts(data_clean4$`return`)
```

### plot the series ###
```{r}
plot(return4)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=return4,order=c(1,1))
mpq1 = garch(x=return4,order=c(1,2))
mpq2 = garch(x=return4,order=c(2,1))
mpq3 = garch(x=return4,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq1),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
res4= residuals(mpq1)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq1)); qqline(residuals(mpq1))
acf(residuals(mpq1)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq1)))
jarque.bera.test(na.omit(residuals(mpq1)))
skewness(na.omit(residuals(mpq1)))
kurtosis(na.omit(residuals(mpq1)))
```

```{R}
gBox(mpq1,x=return4,method='squared')
gBox(mpq1,lags =20,plot = F, x=return4,method='squared')$pvalue
```

# Fifth Dataset COF #

```{r}
data5 = read_xlsx ("ZhiwenXu.xlsx", sheet = 5)
data_clean5 = data5 %>% drop_na()
return5 = as.ts(data_clean5$`return`)
```

### plot the series ###
```{r}
plot(return5)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=return5,order=c(1,1))
mpq1 = garch(x=return5,order=c(1,2))
mpq2 = garch(x=return5,order=c(2,1))
mpq3 = garch(x=return5,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq1),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
res5  = residuals(mpq1)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq1)); qqline(residuals(mpq1))
acf(residuals(mpq1)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq1)))
jarque.bera.test(na.omit(residuals(mpq1)))
skewness(na.omit(residuals(mpq1)))
kurtosis(na.omit(residuals(mpq1)))
```

```{R}
gBox(mpq1,x=return5,method='squared')
gBox(mpq1,lags =20,plot = F, x=return5,method='squared')$pvalue
```


# Sixth Dataset TMO #

```{r}
data6 = read_xlsx ("ZhiwenXu.xlsx", sheet = 6)
data_clean6 = data6 %>% drop_na()
return6 = as.ts(data_clean6$`return`)
```

### plot the series ###
```{r}
plot(return6)
```

### Fit different models

### Best model is Garch(1,1)
```{r, results='hide'}
mpq = garch(x=return6,order=c(1,1))
mpq1 = garch(x=return6,order=c(1,2))
mpq2 = garch(x=return6,order=c(2,1))
mpq3 = garch(x=return6,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
res6 = residuals(mpq)
sum(na.omit(residuals(mpq1))^2)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
skewness(na.omit(residuals(mpq)))
kurtosis(na.omit(residuals(mpq)))
```

```{R}
gBox(mpq,x=return6,method='squared')
gBox(mpq,lags =20,plot = F, x=return6,method='squared')$pvalue
```

# Seventh Dataset UPS #

```{r}
data7 = read_xlsx ("ZhiwenXu.xlsx", sheet = 7)
data_clean7 = data7 %>% drop_na()
return7 = as.ts(-data_clean7$`Neg. log return`)
```

### plot the series ###
```{r}
plot(return7)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=return7,order=c(1,1))
mpq1 = garch(x=return7,order=c(1,2))
mpq2 = garch(x=return7,order=c(2,1))
mpq3 = garch(x=return7,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq1),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
res7 = residuals(mpq1)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq1)); qqline(residuals(mpq1))
acf(residuals(mpq1)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq1)))
jarque.bera.test(na.omit(residuals(mpq1)))
skewness(na.omit(residuals(mpq1)))
kurtosis(na.omit(residuals(mpq1)))
```

```{R}
gBox(mpq1,x=return7,method='squared')
gBox(mpq1,lags =20,plot = F, x=return7,method='squared')$pvalue
```

# Eighth Dataset BIIB #

```{r}
data8 = read_xlsx ("ZhiwenXu.xlsx", sheet = 8)
data_clean8 = data8 %>% drop_na()
return8= as.ts(data_clean8$`return`)
```

### plot the series ###
```{r}
plot(return8)
```

### Fit different models

### Best model is Garch(1,1)
```{r, results='hide'}
mpq = garch(x=return8,order=c(1,1))
mpq1 = garch(x=return8,order=c(1,2))
mpq2 = garch(x=return8,order=c(2,1))
mpq3 = garch(x=return8,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
res8 = residuals(mpq)
sum(na.omit(residuals(mpq1))^2)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
skewness(na.omit(residuals(mpq)))
kurtosis(na.omit(residuals(mpq)))
```

```{R}
gBox(mpq,x=return8,method='squared')
gBox(mpq,lags =20,plot = F, x=return8,method='squared')$pvalue
```

# Ninth Dataset GPS #

```{r}
data9 = read_xlsx ("ZhiwenXu.xlsx", sheet = 9)
data_clean9 = data9 %>% drop_na()
return9 = as.ts(data_clean9$`return`)
```

### plot the series ###
```{r}
plot(return9)
```

### Fit different models

### Best model is Garch(1,1)
```{r, results='hide'}
mpq = garch(x=return9,order=c(1,1))
mpq1 = garch(x=return9,order=c(1,2))
mpq2 = garch(x=return9,order=c(2,1))
mpq3 = garch(x=return9,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
res9 = residuals(mpq)
sum(na.omit(residuals(mpq1))^2)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
skewness(na.omit(residuals(mpq)))
kurtosis(na.omit(residuals(mpq)))
```

```{R}
gBox(mpq,x=return9,method='squared')
gBox(mpq,lags =20,plot = F, x=return9,method='squared')$pvalue
```

# Tenth Dataset IPG #

```{r}
data10 = read_xlsx ("ZhiwenXu.xlsx", sheet = 10)
data_clean10 = data10 %>% drop_na()
return10 = as.ts(data_clean10$`return`)
```

### plot the series ###
```{r}
plot(return10)
```

### Fit different models

### Best model is Garch(2,1)
```{r, results='hide'}
mpq = garch(x=return10,order=c(1,1))
mpq1 = garch(x=return10,order=c(1,2))
mpq2 = garch(x=return10,order=c(2,1))
mpq3 = garch(x=return10,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq2),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
res10 = residuals(mpq3)
```

### diagnostics
```{r}
qqnorm(residuals(mpq2)); qqline(residuals(mpq2))
acf(residuals(mpq2)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq2)))
jarque.bera.test(na.omit(residuals(mpq2)))
skewness(na.omit(residuals(mpq2)))
kurtosis(na.omit(residuals(mpq2)))
```

```{R}
gBox(mpq2,x=return10,method='squared')
gBox(mpq2,lags =20,plot = F, x=return10,method='squared')$pvalue
```

### Step 5

```{r}
new = rep(0,length(return1))
for (i in 1:length(return1)){
new[[i]] = 0.1*return1[i] + 0.1*return2[i] + 0.1*return3[i] + 0.1*return4[i] + 0.1*return5[i]+0.1*return6[i]+0.1*return7[i]+0.1*return8[i]+0.1*return9[i]+0.1*return10[i]
}
```

```{r}
base_mean = mean(new)
base_mean
base_sd = sd(new)
base_sd
```

```{r}
set.seed(0)
max_mean = 0
b1 = rep(0, 8)
b2 = rep(0, 8)
b3 = rep(0, 8)
b4 = rep(0, 8)
b5 = rep(0, 8)
b6 = rep(0, 8)
b7 = rep(0, 8)
b8 = rep(0, 8)
b9 = rep(0, 8)
b10= rep(0, 8)
best_sd = 0
```

```{r}
counter =0
c1 = seq(0,1,by=0.1)
  for (a in 1:length(c1)){
    if (counter == 8){
      break
    }
    c2 = seq(0,1-c1[a],by=0.1)
    for (b in 1:length(c2)){
      if(counter == 8){
        break
      }
      c3 = seq(0,1-c1[a]-c2[b],by=0.1)
      for (c in 1:length(c3)){
        if(counter == 8){
          break
        }
        c4 = seq(0,1-c1[a]-c2[b]-c3[c],by=0.1)
        for(d in 1:length(c4)){
          if(counter == 8){
            break
          }
          c5 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d],by=0.1)
          for(e in 1:length(c5)){
            if(counter == 8){
              break
            }
            c6 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e],by=0.1)
            for (f in 1:length(c6)){
              if(counter == 8){
                break
              }
              c7 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f],by=0.1)
              for(g in 1:length(c7)){
                if(counter == 8){
                break
                }
                c8 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f]-c7[g],by=0.1)
                for (h in 1:length(c8)){
                  if(counter == 8){
                  break
                  }
                  c9 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f]-c7[g]-c8[h],by=0.1)
                  for(j in 1:length(c9)){
                    if(counter == 8){
                    break
                    }
                     c10 = 1-(c1[a] + c2[b] + c3[c] + c4[d] + c5[e]+c6[f]+c7[g]+c8[h]+c9[j])
                         new =rep(0, length(return1))
                         for (i in 1:length(return1)){
                         new[[i]] = c1[a]*return1[i] + c2[b]*return2[i] + c3[c]*return3[i] + c4[d]*return4[i] + c5[e]*return5[i]+c6[f]*return6[i]+c7[g]*return7[i]+c8[h]*return8[i]+c9[j]*return9[i]+c10*return10[i]
                         }
                         mean = mean(new)
                         if ( max_mean <= mean){
                           if( sd (new) <= 0.006174595){
                             max_mean = mean
                             counter  = counter + 1
                             b1[counter] = c1[a] 
                             b2[counter] = c2[b]
                             b3[counter] = c3[c] 
                             b4[counter] = c4[d] 
                             b5[counter] = c5[e]
                             b6[counter] = c6[f]
                             b7[counter] = c7[g]
                             b8[counter] = c8[h]
                             b9[counter] = c9[j]
                             b10[counter] = c10
                             best_sd = sd(new)
                             print(counter)
                             print(best_sd)
                             print(max_mean)
                           }
                         }
                  }
                }
              }
            }
          }
        }
      }
    }
  }
```

```{r}
print(b1)
print(b2)
print(b3)
print(b4)
print(b5)
print(b6)
print(b7)
print(b8)
print(b9)
print(b10)
```

# Step 6

```{r}
new_res1 = res1[8:length(res1)]
new_res2 = res2[8:length(res2)]
new_res3 = res3[8:length(res3)]
new_res4 = res4[8:length(res4)]
new_res5 = res5[8:length(res5)]
new_res6 = res6[8:length(res6)]
new_res7 = res7[8:length(res7)]
new_res8 = res8[8:length(res8)]
new_res9 = res9[8:length(res9)]
new_res10 = res10[8:length(res10)]
```

```{r}
new = rep(0,length(new_res1))
for (i in 1:length(new_res1)){
new[[i]] = 0.1*new_res1[i] + 0.1*new_res2[i] + 0.1*new_res3[i] + 0.1*new_res4[i] + 0.1*new_res5[i]+0.1*new_res6[i]+0.1*new_res7[i]+0.1*new_res8[i]+0.1*new_res9[i]+0.1*new_res10[i]
}
```

```{r}
mean(new)
base_sd = sd(new)
base_sd
```

```{r}
set.seed(0)
max_mean = 0
b1 = rep(0, 8)
b2 = rep(0, 8)
b3 = rep(0, 8)
b4 = rep(0, 8)
b5 = rep(0, 8)
b6 = rep(0, 8)
b7 = rep(0, 8)
b8 = rep(0, 8)
b9 = rep(0, 8)
b10= rep(0, 8)
best_sd = 0
```

```{r}
counter =0
c1 = seq(0,1,by=0.1)
  for (a in 1:length(c1)){
    if (counter == 8){
      break
    }
    c2 = seq(0,1-c1[a],by=0.1)
    for (b in 1:length(c2)){
      if(counter == 8){
        break
      }
      c3 = seq(0,1-c1[a]-c2[b],by=0.1)
      for (c in 1:length(c3)){
        if(counter == 8){
          break
        }
        c4 = seq(0,1-c1[a]-c2[b]-c3[c],by=0.1)
        for(d in 1:length(c4)){
          if(counter == 8){
            break
          }
          c5 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d],by=0.1)
          for(e in 1:length(c5)){
            if(counter == 8){
              break
            }
            c6 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e],by=0.1)
            for (f in 1:length(c6)){
              if(counter == 8){
                break
              }
              c7 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f],by=0.1)
              for(g in 1:length(c7)){
                if(counter == 8){
                break
                }
                c8 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f]-c7[g],by=0.1)
                for (h in 1:length(c8)){
                  if(counter == 8){
                  break
                  }
                  c9 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f]-c7[g]-c8[h],by=0.1)
                  for(j in 1:length(c9)){
                    if(counter == 8){
                    break
                    }
                     c10 = 1-(c1[a] + c2[b] + c3[c] + c4[d] + c5[e]+c6[f]+c7[g]+c8[h]+c9[j])
                         new =rep(0, length(new_res1))
                         for (i in 1:length(new_res1)){
                         new[[i]] = c1[a]*new_res1[i] + c2[b]*new_res2[i] + c3[c]*new_res3[i] + c4[d]*new_res4[i] + c5[e]*new_res5[i]+c6[f]*new_res6[i]+c7[g]*new_res7[i]+c8[h]*new_res8[i]+c9[j]*new_res9[i]+c10*new_res10[i]
                         }
                         mean = mean(new)
                         if ( max_mean <= mean){
                           if( sd (new) <= 0.6163071){
                             counter  = counter + 1
                             max_mean = mean
                             b1[counter] = c1[a] 
                             b2[counter] = c2[b]
                             b3[counter] = c3[c] 
                             b4[counter] = c4[d] 
                             b5[counter] = c5[e]
                             b6[counter] = c6[f]
                             b7[counter] = c7[g]
                             b8[counter] = c8[h]
                             b9[counter] = c9[j]
                             b10[counter] =c10
                             best_sd = sd(new)
                             print(counter)
                             print(best_sd)
                             print(max_mean)
                           }
                         }
                  }
                }
              }
            }
          }
        }
      }
    }
  }

```

```{R}
print(b1)
print(b2)
print(b3)
print(b4)
print(b5)
print(b6)
print(b7)
print(b8)
print(b9)
print(b10)
```

# Step 7

```{r}
p1 = data_clean1$Close
p2 = data_clean2$Close
p3 = data_clean3$Close
p4 = data_clean4$Close
p5 = data_clean5$Close
p6 = data_clean6$Close
p7 = data_clean7$Close
p8 = data_clean8$Close
p9 = data_clean9$Close
p10 = data_clean10$Close
```

```{r}
base= rep(0,length(p1)-1)
for (i in 1:(length(p1)-1)){
base[[i]] = log((0.1*p1[i+1]+0.1*p2[i+1]+0.1*p3[i+1]+0.1*p4[i+1]+0.1*p5[i+1]+0.1*p6[i+1]+0.1*p7[i+1]+0.1*p8[i+1]+0.1*p9[i+1]+0.1*p10[i+1])/(0.1*p1[i]+0.1*p2[i]+0.1*p3[i]+0.1*p4[i]+0.1*p5[i]+0.1*p6[i]+0.1*p7[i]+0.1*p8[i]+0.1*p9[i]+0.1*p10[i]))
}
```

```{r}
mean(base)
base_sd = sd(base)
base_sd
```

```{r}
set.seed(0)
max_mean = 0
b1 = rep(0, 8)
b2 = rep(0, 8)
b3 = rep(0, 8)
b4 = rep(0, 8)
b5 = rep(0, 8)
b6 = rep(0, 8)
b7 = rep(0, 8)
b8 = rep(0, 8)
b9 = rep(0, 8)
b10= rep(0, 8)
best_sd = 0
```

## Optimization Procedure

0. Create and initialize variables that will be used: max_mean, best_sd, and b1,…,b9. Max_mean is used to keep track of current maximized means in loops, and will be updated if a larger mean appears. Best_sd keeps tracks the current sd of best combination of c1,…,c10. B1,…,b9 are to store the values of possible c1,…,c9 generated in the loops.
1. Create sequences as possible values for each c. For example, c1 is created by seq(0,1-c1-c2,by=0.1), and is (0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1.0). 
2. Loop through each sequence and then we have different combinations of c1, c2, …, c10. 
3. Note: Step 2 and Step 1 is implemented at the same time since the c1+c2+…+c10 = 1. I created (0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1.0) for c1, and then in the loop of c1, I created the sequences for c2(which will depend on c1 since c2<=1-c1). And c3 is created by seq(0,1-c1-c2,by=0.1), and so on. c10 is then 1-c1-c2-c3-…-c9.
4. For each combination of possible values of c1, …, c9 that sum up to 1, I calculated the new time series from the equation, and then calculated the mean and variance. If variance is smaller than std(1/10,1/10, . . . ,1/10), and mean is larger than current max, current max mean will  updated, and standard deviation of new series, and c1,c2,..,c9 will be saved and printed out.
5. The last max_mean, best_sd, and b1,…,b9 are what we want.


```{r}
counter =0
c1 = seq(0,1,by=0.1)
  for (a in 1:length(c1)){
    if (counter == 8){
      break
    }
    c2 = seq(0,1-c1[a],by=0.1)
    for (b in 1:length(c2)){
      if(counter == 8){
        break
      }
      c3 = seq(0,1-c1[a]-c2[b],by=0.1)
      for (c in 1:length(c3)){
        if(counter == 8){
          break
        }
        c4 = seq(0,1-c1[a]-c2[b]-c3[c],by=0.1)
        for(d in 1:length(c4)){
          if(counter == 8){
            break
          }
          c5 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d],by=0.1)
          for(e in 1:length(c5)){
            if(counter == 8){
              break
            }
            c6 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e],by=0.1)
            for (f in 1:length(c6)){
              if(counter == 8){
                break
              }
              c7 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f],by=0.1)
              for(g in 1:length(c7)){
                if(counter == 8){
                break
                }
                c8 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f]-c7[g],by=0.1)
                for (h in 1:length(c8)){
                  if(counter == 8){
                  break
                  }
                  c9 = seq(0,1-c1[a]-c2[b]-c3[c]-c4[d]-c5[e]-c6[f]-c7[g]-c8[h],by=0.1)
                  for(j in 1:length(c9)){
                    if(counter == 8){
                    break
                    }
                     c10 = 1-(c1[a] + c2[b] + c3[c] + c4[d] + c5[e]+c6[f]+c7[g]+c8[h]+c9[j])
                         new =rep(0, length(p1)-1)
                         for (i in 1:(length(p1)-1)){
                         new[i] = log((c1[a]*p1[i+1]+c2[b]*p2[i+1]+c3[c]*p3[i+1]+c4[d]*p4[i+1]+c5[e]*p5[i+1]+c6[f]*p6[i+1]+c7[g]*p7[i+1]+c8[h]*p8[i+1]+c9[j]*p9[i+1]+c10*p10[i+1])/(c1[a]*p1[i]+c2[b]*p2[i]+c3[c]*p3[i]+c4[d]*p4[i]+c5[e]*p5[i]+c6[f]*p6[i]+c7[g]*p7[i]+c8[h]*p8[i]+c9[j]*p9[i]+c10*p10[i]))
                         }
                         mean = mean(new)
                         if ( max_mean <= mean){
                           if( sd (new) <= 0.0139621){
                             counter  = counter + 1
                             max_mean = mean
                             b1[counter] = c1[a] 
                             b2[counter] = c2[b]
                             b3[counter] = c3[c] 
                             b4[counter] = c4[d] 
                             b5[counter] = c5[e]
                             b6[counter] = c6[f]
                             b7[counter] = c7[g]
                             b8[counter] = c8[h]
                             b9[counter] = c9[j]
                             b10[counter] =c10
                             best_sd = sd(new)
                             print(counter)
                             print(best_sd)
                             print(max_mean)
                           }
                         }
                  }
                }
              }
            }
          }
        }
      }
    }
  }

```

```{R}
print(b1)
print(b2)
print(b3)
print(b4)
print(b5)
print(b6)
print(b7)
print(b8)
print(b9)
print(b10)
```

# Step 8

```{r}
base_ts = as.ts(base)
```

### plot the series ###
```{r}
plot(base_ts)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=base_ts,order=c(1,1))
mpq1 = garch(x=base_ts,order=c(1,2))
mpq2 = garch(x=base_ts,order=c(2,1))
mpq3 = garch(x=base_ts,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq1),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq1)); qqline(residuals(mpq1))
acf(residuals(mpq1)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq1)))
jarque.bera.test(na.omit(residuals(mpq1)))
skewness(na.omit(residuals(mpq1)))
kurtosis(na.omit(residuals(mpq1)))
gBox(mpq1,x=base_ts,method='squared')
gBox(mpq1,lags =20,plot = F, x=base_ts,method='squared')$pvalue
```

### Computer mean and sd for residuals

```{r}
mean(na.omit(residuals(mpq1)))
sd(na.omit(residuals(mpq1)))
```

# Step 9

### c = (0 0 0 0 0 0.2 0.1 0.1 0.3 0.3)

```{r}
best= rep(0,length(p1)-1)
for (i in 1:(length(p1)-1)){
best[[i]] = log((0.2*p6[i+1]+0.1*p7[i+1]+0.1*p8[i+1]+0.3*p9[i+1]+0.3*p10[i+1])/(0.2*p6[i]+0.1*p7[i]+0.1*p8[i]+0.3*p9[i]+0.3*p10[i]))
}
```

### plot the series ###
```{r}
best_ts = as.ts(best)
plot(best_ts)
```

### Fit different models

### Best model is Garch(1,2)
```{r, results='hide'}
mpq = garch(x=best_ts,order=c(1,1))
mpq1 = garch(x=best_ts,order=c(1,2))
mpq2 = garch(x=best_ts,order=c(2,1))
mpq3 = garch(x=best_ts,order=c(2,2))
```

```{r}
summary(mpq)
summary(mpq1)
summary(mpq2)
summary(mpq3)
```

### plot residuals ###

```{r}
plot(residuals(mpq3),type='h',ylab='standardized residuals')
```

### sum of squared residuals ###

```{r}
sum(na.omit(residuals(mpq))^2)
sum(na.omit(residuals(mpq1))^2)
sum(na.omit(residuals(mpq2))^2)
sum(na.omit(residuals(mpq3))^2)
```

### diagnostics
```{r}
qqnorm(residuals(mpq3)); qqline(residuals(mpq3))
acf(residuals(mpq3)^2,na.action=na.omit)
shapiro.test(na.omit(residuals(mpq3)))
jarque.bera.test(na.omit(residuals(mpq3)))
skewness(na.omit(residuals(mpq3)))
kurtosis(na.omit(residuals(mpq3)))
gBox(mpq1,x=best_ts,method='squared')
gBox(mpq1,lags =20,plot = F, x=best_ts,method='squared')$pvalue
```

### Computer mean and sd for residuals

```{r}
mean(na.omit(residuals(mpq3)))
sd(na.omit(residuals(mpq3)))
```